equations

### 2023-05-31 Manuscript.Rmd
last_cleaning

#plot parameterrecovery
load(files[[1]])
q = lapply(here("scripts", scripts), source)
kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5)
load(files[[2]])
q = lapply(here("scripts", scripts), source)
logisticplot = plot_parameterrecovery(rw_pp_logs, div = F, subs = 5)
load(files[[3]])
q = lapply(here("scripts", scripts), source)
rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
load(files[[4]])
q = lapply(here("scripts", scripts), source)
wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)

@@

@@

>>>>

#plot parameterrecovery
load(files[[1]])
q = lapply(here("scripts", scripts), source)
kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5, "Kalman filter")
load(files[[2]])
q = lapply(here("scripts", scripts), source)
logisticplot = plot_parameterrecovery(rw_pp_logs, div = F, subs = 5,"Logistic RW")
load(files[[3]])
q = lapply(here("scripts", scripts), source)
rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5,"Rescorla Wagner")
load(files[[4]])
q = lapply(here("scripts", scripts), source)
wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5,"Weighted bayes")

@@

```{r getting temperatures}

# Create a function to assign temperature indicator based on a threshold
assign_indicator <- function(temperature, threshold) {
  ifelse(temperature <= threshold, "Low", "High")
}

# Calculate the threshold for each ID and session
df$threshold <- ave(df$temperature, df$id, df$session, FUN = median)

# Create the indicator column
df$temperature_indicator <- mapply(assign_indicator, df$temperature, df$threshold)
```

@@

df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
  rename_all(tolower) %>%
  filter(trial != 0) %>%
  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
  mutate_all(replace_na, 0)git

### 2023-05-31 equations.Rmd
last_cleaning

---
title: "equations"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

@@

$$
\begin{equation}
(1-\gamma) = \frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
\end{equation}
$$
Now uterlising the fact that if $x = \frac{a}{b}$ then $1-x = \frac{(b-a)}{b}$

@@

>>>>

---
title: "equations"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

@@

$$
\begin{equation}
(1-\gamma) = \frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
\end{equation}
$$
Now use the fact that if $x = \frac{a}{b}$ then $1-x = \frac{(b-a)}{b}$

@@

The same logic goes for equation (16)
